A comparison of different methods for calculating tangent-stiffness matrices in a massively parallel computational peridynamics code.

### 2013-09-04 jacobian_calc_CMAME.tex
Spelling errors

\section{Methods and Materials} \subsection{Material: Perdynamics Code}
\subsubsection{\emph{Perdigm} and Peridynamics} 
\subsubsection{Implementing Complex-Step in \emph{Peridigm}}

@@

What was recorded during the test runs as experimental data is the subject the following
subsubsection. It is organized to eplain "what", "why" and "how" in that order.

>>>>

\section{Methods and Materials}

\subsection{Material: Perdynamics Code}

The following subsubsections identify the program modified to run the simulations for the
comparative study and explain what modifications were necessary.

\subsubsection{\emph{Perdigm} and Peridynamics} 
\subsubsection{Implementing Complex-Step in \emph{Peridigm}}

@@

What was recorded during the test runs as experimental data is the subject the following
subsubsection. It is organized to explain "what", "why" and "how" in that order.
